Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2021-11-29 article.rnw
Fix a pair of swapped words.
Swap alpha_{ij} and N_j in the model formulation.
To conform to standard notation.

Models have long been used in ecology community \parencite{lotka1925elements}.
They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide.

@@

I fitted the Lotka--Volterra competition model to the data.
As the response variable was fecundity, I used a discrete-time version of the model, as follows:
\[
	N_{i,t+1} = N_{i,t} r_i \left(1 - \sum_j N_{j,t} \alpha_{ij}\right)
,\]
where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ upon species $i$.
$N_{i,t+1}$ is the size of the population in the following time-step, i.e.\ the number of surviving offspring, the fecundity, of the previous generation, and therefore is equal to the experimentally measured response variable.
The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.

@@

The models were fitted to the data using maximum likelihood regression techniques.
Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
As such, I assumed a normal error distribution, and fitted a least squares regression.
To prevent heteroskedasticity, I used the \emph{per capita} fecundity as the response variable, as in the following model:
\[
	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j N_{j,t} \alpha_{ij}\right)
.\]

>>>>

Models have long been used in community ecology \parencite{lotka1925elements}.
They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide.

@@

I fitted the Lotka--Volterra competition model to the data.
As the response variable was fecundity, I used a discrete-time version of the model, as follows:
\[
	N_{i,t+1} = N_{i,t} r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
,\]
where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ upon species $i$.
$N_{i,t+1}$ is the size of the population in the following time-step, i.e.\ the number of surviving offspring, the fecundity, of the previous generation, and therefore is equal to the experimentally measured response variable.
The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.

@@

The models were fitted to the data using maximum likelihood regression techniques.
Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
As such, I assumed a normal error distribution, and fitted a least squares regression.
To prevent heteroskedasticity, I used the \emph{per capita} fecundity as the response variable, as in the following model:
\[
	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
.\]
